Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-22 manuscript/main.tex
theory done, twice
overleaf import

		\max_{ \boldsymbol{ \alpha } } 

@@

		\boldsymbol{\alpha}, \mathbf{Z}_i

@@

		\bigr)~\text{s.t.}~\| \boldsymbol{\alpha} \|_2 = 1,~\boldsymbol{\alpha}^\top  \widehat{\operatorname{Cov}}^2

@@

	where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively. A standard algorithm for solving this problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.

@@

	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
	    \jongmin{comment:maybe we can move this section to precede the algorithm section. then the new structure will introduce population version first and introduce finite-sample estimation procedure.}
	The fundamental property of classical scalar PLS is that the PLS component direction  corresponds to the first eigenvector of the squared covariance matrix, satisfying  the Tucker's Criterion \citep{Tucker1938}.
	Under a mild assumption,
	We derive an analogous result  in our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}.
	This justifies our estimation procedure introduced in Section \ref{section:main:our_algorithm}.
For notational simplicity, we omit the index $l$. At the population level, where the random objects are fully observed, it suffices to consider $Y_1$ and $W_1$ rather than their sampled realizations.
We assume 
$\mathbb{E}[Y_1]=0 \in \mathbb{R}$ and $\mathbb{E}[W_1] = 0 \in \mathbb{H}$.
 We first define the cross-covariance between the response and the functional predictors, where the predictors correspond to the observed versions for $l=1$ and to the residualized versions for $l \ge 2$:
	\begin{equation}\label{def:cross_covariance_yx}
		\sigma_{YX}
		=
		\bigl(
		\sigma_{YX, 1}(t) , \ldots, \sigma_{YX, K}(t) 
		\bigr)
		:=
		\bigl(
		\mathbb{E}
		[Y_1 X_{11}]
		,\ldots, 
		\mathbb{E}
		[Y_1  X_{1K}]
		\bigr)   \in \mathcal{F}^{\otimes K},
	\end{equation}
	and between the response and the scalar predictor:
	\begin{equation*}
		\sigma_{YZ} 
		= 
		(\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top 
		:= 
		\bigl(
		\mathbb{E}[Y_1 Z_{11}]
		,\ldots,
		\mathbb{E}[Y_1 Z_{1p}]
		\bigr)^\top %= E(Y\mathbf{Z})
		\in \mathbb{R}^p.
	\end{equation*}
	Based on these definitions, we define the cross-covariance term between the response and the hybrid predictor as
	\begin{equation*}
		\Sigma_{YW} :=  
		\mathbb{E}
		[ Y_1 W_1 ]
		=
		\bigl(
		\sigma_{YX, 1} , \ldots, \sigma_{YX, K} , \, \sigma_{YZ}
		\bigr) \in \mathbb{H}.
	\end{equation*}
	Based on these definitions, we introduce two cross-covariance operators and their properties.
	\begin{lemma}\label{lemma:cross_cov_functional}
		Define the operator $
		\mathcal{C}_{YW}
		=
		\mathbb{E}(W_1 \otimes_\mathbb{H} Y_1)
		: \mathbb{H} \rightarrow \mathbb{R}$ such that for any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$, it maps $h$ to a real number as: \begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W_1, h \rangle_\mathbb{H} Y_1 \right] = \langle \Sigma_{YW}, h \rangle_\mathbb{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX, k}(t) \, f_k(t) \, dt + \sigma_{YW}^\top \mathbf{v}. \end{equation*} 
		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact. This way, we don't need uniform continuiity of $\sigma_{YX}$.}If there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}\label{condition_for_compact}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		the operator $\mathcal{C}_{YW}$ is a compact operator.
	\end{lemma}
	Proof of Lemma \ref{lemma:cross_cov_functional}
	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
	\begin{lemma}\label{lemma:cross_cov_operator}
		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]: \mathbb{R} \rightarrow \mathbb{H}$,
		which	maps  $d \in \mathbb{R}$ to a hybrid object in $\mathbb{H}$ as follows:
		%%%%
		\begin{align*}		
			\mathcal{C}_{WY} d 
			:= 
			\mathbb{E} 
			\bigl[
			\langle Y_1, d \rangle W_1 
			\bigr] 
			= 
			\mathbb{E}
			[ Y_1 W_1 d ] =  d \, \Sigma_{Y W}.
		\end{align*}
		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
	\end{lemma}

	The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.

	Based on these two operators, we define a positive   operator as follows:
	\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
		Define
		$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{H}$ as an operator which performs the following mapping:
		\begin{equation*}
			\mathcal{U} h 
			= 
			\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
			=
			\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathbb{H}) 
			=  
			\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathbb{H} 
			= 
			(\Sigma_{YW} \otimes \Sigma_{YW}) h.
		\end{equation*}
		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
		Then $\mathcal{U}$
		is a self-adjoint and positive-semidefinite operator.
		Under the conditions of Lemma \ref{lemma:cross_cov_functional}, $\mathcal{U}$ is a compact operator.
	\end{lemma}
	The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Lemma \ref{lemma:composite_cross_cov} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathbb{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following theorem introduces the population-level PLS and Tucker's Criterion, adapted to our scalar-on-hybrid regression model setting, based on the aforementioned operators defined in the hybrid space.
	\begin{theorem}[Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
		\begin{equation*} 
			\max \limits_{\substack{\xi \in \mathbb{H} \\ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W_1 , \, \xi \rangle_\mathbb{H}, Y_1 \right)
		\end{equation*} 
		is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
	\end{theorem}
	Note that the maximizer is a deterministic element of $\mathbb{H}$.
	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.

Let 
 $\mathcal{U}^{[l]} := \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$,
 where
 $\Sigma_{YW}^{[l]} = E(Y_1^{[l]}  W_1^{[l]})$
 is formulated   using the $l$-th residualized response and predictors.
 Assuming that $\mathcal{U}^{[l]}$
   satisfies the conditions of Lemma \ref{lemma:cross_cov_functional},
	the $l$-th PLS direction $\xi^{[l]}$ can be obtained as the \textit{first} eigenfunction of  $\mathcal{U}^{[l]}$.

\jongmin{comment: I added the following properties, motivated by Proposition 4 of \citet{predaPLSRegressionStochastic2005} and section 2 of \citet{aguileraPenalizedVersionsFunctional2016}. }

\begin{lemma} \label{lem:regression_W_rho} The population-level least square regression coefficient of regressing $W_1^{[l]}$ on its score $\rho_1^{[l]} = \langle W_1^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}}$ is $\mathbf{\xi^{[l]}} \in \mathbb{H}$. This coefficient is used in the residualization process as follows: \begin{align*} W_1^{[l]} &= W_1^{[l-1]} - \langle W_1^{[l-1]}, \xi^{[l-1]} \rangle_{\mathbb{H}} \xi^{[l-1]},\end{align*} where  $W_1^{[1]} = W_1$. \end{lemma} 
Proof of Lemma \ref{lem:regression_W_rho} is provided in Appendix \ref{section:proof:lem:regression_W_rho}.

 We define an operator $\mathcal{T}$ that maps an element $g \in \mathbb{H}$   (representing a potential regression coefficient) to the predicted response.
\begin{lemma}\label{lemma:tau_ast}
	Define the linear operator $\mathcal{T}: \mathbb{H} \to \mathbb{R}$ that maps  $g \in \mathbb{H}$ to 
	$
	\mathcal{T}g = \langle W, g \rangle_{\mathbb{H}}
	$.
 Let $\mathcal{T}^\ast: \mathbb{R} \to \mathbb{H}$ denote its adjoint operator. Then,
	\[
	\Sigma_{YW}^{[1]} = \mathcal{T}^\ast Y.
	\]
\end{lemma}
Proof of Lemma \ref{lemma:tau_ast} is provided in Appendix \ref{section:rpoof:lemma:tau_ast}.

\begin{proposition}\label{proposition:pls_direction_in_range_T_ast}
	All PLS Directions Reside in $R(\mathcal{T}^\ast  )$
\end{proposition}
 Proof of Proposition \ref{proposition:pls_direction_in_range_T_ast} is provided in Appendix \ref{section:proof:proposition:pls_direction_in_range_T_ast}

\begin{proposition}
	\label{proposition:CONS}
	The set of PLS directions $\{\xi^{[l]}\}_{l=1}^\infty$ forms a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$.
\end{proposition}
Proof of Proposition \ref{proposition:CONS}
is provided in Appendix \ref{section:proof:proposition:CONS}.

\begin{corollary}
	\label{cor:orthogonal_scores}
	Given that $\{\xi^{[l]}\}_{l=1}^\infty$ is a complete orthonormal system (CONS) for $R(\mathcal{T}^*)$, the corresponding PLS scores $\rho^{[l]}$ can be equivalently expressed as $\rho^{[l]} = \langle W^{[l]}, \xi^{[l]} \rangle_{\mathbb{H}} = \langle W, \xi^{[l]} \rangle_{\mathbb{H}}$. Furthermore, the set of PLS scores $\{\rho^{[l]}\}_{l=1}^\infty$ forms an orthogonal system, that is, for any $j \neq l$, $\mathbb{E}[\rho^{[j]} \rho^{[l]}] = 0$.
\end{corollary}
Let $\beta_{\mathrm{OLS}}$ denote a minimizer of  the mean squared error $ \mathbb{E}[\|Y - \langle \beta, W \rangle_{\mathbb{H}}\|_2^2]$. It
satisfies the normal equation
\begin{equation}\label{normal_equation}
	\mathbb{E}[(Y - \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}})W] = 0 \in \mathbb{H}.
\end{equation}
If the operator $\mathcal{T}^\ast \mathcal{T}$ is invertible,  the minimizer is uniquely determined as 
$\beta_{\mathrm{OLS}} = (\mathcal{T}^\ast \mathcal{T})^{-1} \mathcal{T}^\ast Y$.
\begin{proposition}\label{proposition:nu_l}
	At the $l$-th iteration, the 
	population level least square regression coefficient of the residual response $Y^{[l]}$ on the score $\rho^{[l]}$ is defined as:
	$$\nu^{[l]} = \langle \beta_{\mathrm{OLS}}, \xi^{[l]} \rangle_{\mathbb{H}}.$$
\end{proposition}
Proof of Proposition \ref{proposition:nu_l} is provided in Appendix \ref{section:proof:proposition:nu_l}.

The following theorem states that the fitted values from hybrid PLS converge to those of ordinary linear regression in the mean-squared sense. This shows that hybrid PLS, as a dimension-reduction technique, can effectively capture the predictive power of a full linear model when a sufficient number of components is used.
\begin{theorem}[$L^2$ Convergence of Hybrid PLS at Population Level]\label{thm:hybrid_pls_convergence}
	 Define $Y_{\mathrm{OLS}} = \langle \beta_{\mathrm{OLS}}, W \rangle_{\mathbb{H}}$ as the population-level ordinary linear regression fitted value. Let $Y_{\mathrm{PLS}, L} = \sum_{l=1}^L \nu^{[l]} \rho^{[l]}$ be the Hybrid PLS fitted value with $L$ components. Then, the Hybrid PLS fitted value converges to the ordinary linear regression fitted value in the mean-squared sense:
	\begin{equation*}
		\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y_{\mathrm{OLS}} \|_2^2 \right] = 0
	\end{equation*}
\end{theorem}
 The proof of Theorem \ref{thm:hybrid_pls_convergence} is provided in Appendix \ref{section:proof:thm:hybrid_pls_convergence}.

	\subsection{Geometric properties}\label{section:sub:geom}
	A fundamental property of partial least squares   is that between iterations, its derived directions are orthonormal and PLS scores are orthogonal. Our regularized estimates preserve this property, with respect to a modified inner product that incorporates the roughness penalty, defines as follows:
	\begin{definition}[Roughness-sensitive inner product]\label{def:hybrid_inner_product_roughness}
		Given two hybrid predictors $W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$ and $W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, both elements of $\mathbb{H}$ as defined in Definition \ref{def:hybrid_predictor}, and a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, the roughness-sensitive inner product between $W_1$ and $W_2$ is defined as:
		\begin{equation}		\label{eq: hybrid inner product_roughness}
			\langle W_1, W_2\rangle_{\mathbb{H}, \Lambda}
			:=
			\sum \limits_{k=1}^K \int_0^1 X_{1k}(t) X_{2k}(t) \, dt
			+
			\sum \limits_{k=1}^K \lambda_k \int_0^1 X^{\prime \prime}_{1k}(t) X^{\prime \prime}_{2k}(t) \, dt
			+
			\mathbf{Z}_1^\top \mathbf{Z}_2.
		\end{equation}
	\end{definition}
	Based on this inner product, the following proposition states that the PLS component directions estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal.
	\begin{proposition}[Orthonormality of estimated PLS component directions]\label{proposition: modified orthnormality of PLS components}
		The PLS component directions $
		\widehat{\xi}^{[1]}, \widehat{\xi}^{[2]}, \ldots, \widehat{\xi}^{[L]}
		$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathbb{H}, \Lambda}$. That is,
		\begin{equation*}
			\langle \widehat{\xi}^{[l_1]}, \widehat{\xi}^{[l_2]} \rangle_{\mathbb{H}, \Lambda}
			= \mathbbm{1}(l_1 = l_2), \quad l_1, l_2 = 1, \ldots, L.
		\end{equation*}
	\end{proposition}
	The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.

@@

	The First Eigenfunction $\xi^{[1]}$ Resides in $R(\mathcal{T}^\ast  )$

>>>>

	\begin{equation}\label{scalar_PLS_sample}
		\max_{ \mathbf{ h } } 

@@

		\mathbf{ h }, \mathbf{Z}_i

@@

		\bigr)~\text{s.t.}~\| \mathbf{ h } \|_2 = 1,~\mathbf{ h }^\top  \widehat{\operatorname{Cov}}^2

@@

	where the two $\widehat{\operatorname{Cov}}^2$ denote sample cross-covariance and sample covariance, respectively. A standard algorithm for solving this optimization problem, called nonlinear iterative partial least squares (NIPALS) is presented in Algorithm \ref{alg:scalar_pls}.

@@

	\subsection{ Tucker's Criterion  }\label{section:sub:tucker} 
	\jongmin{comment:maybe we can move this section to precede the algorithm section. then the new structure will introduce population version first and introduce finite-sample estimation procedure.}
	We now derive the population analogue of Algorithm~\ref{alg:hybrid_pls} and establish its key mathematical properties, namely the orthogonality of the PLS directions and scores, as well as convergence to the true response. At the population level, where the random objects are fully observable, we may drop the sample index $i$ and simply work with $Y$
	and
	$W = (X_1, \ldots, X_K, Z_1, \ldots, Z_p)$. Throughout this section we assume 
	$\mathbb{E}[Y] = 0 \in \mathbb{R}$ and $\mathbb{E}[W] = 0 \in \mathbb{H}$.

	The core optimization problem in PLS is formulated in terms of maximizing the squared cross-covariance. At the population level, this quantity is naturally characterized by cross-covariance operators, which we define next. For notational simplicity, we suppress the iteration index $l$, with the understanding that for $l=1$ the predictors correspond to the original variables, while for $l \geq 2$ they represent the residualized versions.
	\begin{definition}\label{def:cross_cov_terms}
		The covariance operator of the hybrid predictor $W$ is denoted as $\Sigma_{W} := \mathbb{E}[W \otimes W]$, so that for $u,v \in \mathbb{H}$, we have
		\[
		\Sigma_{W} u = \mathbb{E}[
		\langle W, u\rangle_{\mathbb{H}}W
		],
		\quad
		\langle \Sigma_{W} u, v \rangle_{\mathbb{H}}
		= \mathbb{E}[\langle W,u \rangle_{\mathbb{H}} \, \langle W,v \rangle_{\mathbb{H}}].
		\]

		The cross-covariances between the response $Y$ and the predictors are
		\[
		\sigma_{YX}
		:=
		\bigl(\mathbb{E}[Y X_{1}],\ldots,\mathbb{E}[Y X_{K}]\bigr) \in \mathcal{F}^{K},
		\quad
		\sigma_{YZ} 
		:=
		\bigl(\mathbb{E}[Y Z_{1}],\ldots,\mathbb{E}[Y Z_{p}]\bigr)^\top \in \mathbb{R}^p.
		\]

		The cross-covariance between $Y$ and the hybrid predictor $W$ is then
		\[
		\Sigma_{YW} := \mathbb{E}[ Y W ] = \bigl( \sigma_{YX}, \, \sigma_{YZ} \bigr) \in \mathbb{H}.
		\]
	\end{definition}
	At the population level, Algorithm \ref{alg:hybrid_pls} without regularizaiton can be expressed as follows.
	Let $W^{[1]} := W$ and $Y^{[1]} := Y$.
	For any   integer $l \geq 2$,
	to be the residuals of the

	where

	which is attained by the leading eigenfunction of the operator 
	$\mathcal{U}^{[l-1]}$, defined analogously to Lemma~\ref{lemma:composite_cross_cov} 
	using $W^{[l-1]}$ and $Y^{[l-1]}$, provided the conditions in 
	Lemma~\ref{lemma:cross_cov_functional} are satisfied.
	\begin{definition}[Population PLS]\label{def:population_pls}
		The population analogue of the PLS optimization problem \eqref{scalar_PLS_sample} in the hybrid space is formulated as the constrained generalized eigenproblem:
		\begin{equation}\label{const_eigen_pop}
			\xi^{[l]} = \arg\max_{h \in \mathbb{H}}
			\operatorname{Cov}^2(\langle W, h \rangle_{\mathbb{H}}, Y),~s.t.~\|h\|_{\mathbb{H}}=1, \langle h, \Sigma_W \, \xi^{[j]} \rangle_{\mathbb{H}} = 0,\, j < l.
		\end{equation}
	\end{definition}
	As in scalar case, this problem can be solved by an iterative algorithm, and yields orthogonal scores:
	\begin{proposition}[Properties of population PLS]
		\label{prop:residualization_equiv_eigen}
		The solution of optimization problem \eqref{const_eigen_pop} of Definition \ref{def:population_pls} is equivalent to that of population NIPALS (Algorithm \ref{alg:population_pls}).  For every \(s\ge 1\) and every \(j\le s-1\), we have
		$
		\mathbb{E}[\rho^{[j]}\rho^{[s]}]=0
		$
		and
		$
		\mathbb{E}[Y^{[s]}\rho^{[j]}]=0.
		$

	\end{proposition}
	Proof of Proposition \ref{prop:residualization_equiv_eigen} is provided in Appendix \ref{section:proof:prop:residualization_equiv_eigen}.
	\begin{algorithm} 
		\caption{Population NIPALS}\label{alg:population_pls}
		\begin{algorithmic}[1]
			\State
			$(W^{[1]}, Y^{[1]} \leftarrow (W, Y)$
			\For{$l = 1, 2, \ldots, L$}
			\State
			$
			\xi^{[l]}
			\leftarrow
			\arg\max_{h \in \mathbb{H}} \operatorname{Cov}^2(\langle W^{[l]}, h \rangle_{\mathbb{H}}, Y^{[l]})~s.t.~ \|h\|_{\mathbb{H}} = 1,
			$\label{alg:line:pls_direction} \Comment{PLS direction}
			%%%%%%%%%
			\State 
			$
			\rho^{[l]} \leftarrow \langle \xi^{[l]}, W^{[l]} \rangle 
			$ \Comment{PLS score}
			%%%%%%%%%%
			\State
			$
			\delta^{[l]}
			\leftarrow
			\frac{1}{\mathbb{E}[ (\rho^{[l]})^2 ]}  \mathbb{E}[W^{[l]} \rho^{[l]}]
			$\label{population_delta}
			\Comment{Linear regression of 
				$W^{[l]}$
				on $\rho^{[l]}$}
			%%%%%%%%%%%
			\State
			$
			\nu^{[l]}
			\leftarrow
			\frac{1}{\mathbb{E}[ (\rho^{[l]})^2 ]}
			\mathbb{E}[Y^{[l]} \rho^{[l]}]
			$
			\Comment{
				Linear regression of 
				$Y^{[l]} $
				on $\rho^{[l]}$
			}
			%%%%%%%%%%%%%%%%%%%
			\State 
			$ W^{[l+1]} \leftarrow W^{[l]} - \rho^{[l]} \, \delta^{[l]}$
			\label{population_predictor_residualize}
			\Comment{
				Residualized predictor
			}
			\State
			$ Y^{[l]} \leftarrow Y^{[l-1]} - \nu^{[l-1]} \, \rho^{[l-1]}$
			\Comment{
				Residualized response
			}
			\EndFor
			\State \textbf{Output:}
			PLS directions $\xi^{[1]}, \ldots, \xi^{[L]}$
		\end{algorithmic}
	\end{algorithm}

	We show that problem \eqref{const_eigen_pop} and Algorithm \ref{alg:population_pls} are well-defined under mild conditions by  establishing that line \ref{alg:line:pls_direction} of Algorithm \ref{alg:population_pls} is well-defined under mild conditions. For clarity, we define the relevant operators while omitting the iteration index for the residualized predictors and responses.
	\begin{lemma}\label{lemma:cross_cov_functional}
		Define the operator $
		\mathcal{C}_{YW}$ such that for   any $h=(f_1, \ldots, f_K, \mathbf{v}) \in \mathbb{H}$,
		\begin{equation*} \mathcal{C}_{YW} h := \mathbb{E} \left[ \langle W, h \rangle_\mathbb{H} Y \right] = \langle \Sigma_{YW}, h \rangle_\mathbb{H} \in \mathbb{R}.
		\end{equation*} 
		\jongmin{instead of showing $\mathcal{U}$ is compact, let's show $\mathcal{C}_{YW}$ is compact. This way, we don't need uniform continuiity of $\sigma_{YX}$.}
		If 
		$\sigma_{YX}$ and $\sigma_{YZ}$ are bounded in the sense that
		there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}\label{condition_for_compact}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \mathbb{E}
			[Y X_{k}](t)^2 < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \mathbb{E}
			[Y Z_{r}]^2 < Q_2,
		\end{align}
		the operator $\mathcal{C}_{YW}$ is a compact operator.
	\end{lemma}
	Proof of Lemma \ref{lemma:cross_cov_functional}
	is provided in Appendix \ref{section:proof:lemma:cross_cov_functional}.
	\begin{lemma}\label{lemma:cross_cov_operator}
		Define $\mathcal{C}_{WY} = \mathbb{E}[Y \otimes W]$,
		such that for any  $d \in \mathbb{R}$,
		%%%%
		\begin{align*}		
			\mathcal{C}_{WY} d 
			:= 
			\mathbb{E} 
			\bigl[
			\langle Y, d \rangle W 
			\bigr] 
			= 
			\mathbb{E}
			[ Y W d ] =  d \, \Sigma_{Y W} \in \mathbb{H}.
		\end{align*}
		Then	$\mathcal{C}_{WY}$ is an adjoint operator of $\mathcal{C}_{YW}$. That is, $\mathcal{C}_{WY} = \mathcal{C}_{YW}^\ast$.
	\end{lemma}	
	The proof of Lemma \ref{lemma:cross_cov_operator} is provided in Appendix \ref{section:proof:lemma:cross_cov_operator}.

	\begin{lemma}[Composite cross-covariance operator]\label{lemma:composite_cross_cov}
		Define
		$\mathcal{U} := \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathbb{H} \rightarrow \mathbb{H}$ as an operator which performs the following mapping:
		\begin{equation*}
			\mathcal{U} h 
			= 
			\mathcal{C}_{WY} ( \mathcal{C}_{YW} h) 
			=
			\mathcal{C}_{YW} (\langle \Sigma_{YW}, h \rangle_\mathbb{H}) 
			=  
			\Sigma_{YW} \, \langle \Sigma_{YW}, h \rangle_\mathbb{H} 
			= 
			(\Sigma_{YW} \otimes \Sigma_{YW}) h.
		\end{equation*}
		In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$.
		Then $\mathcal{U}$
		is a self-adjoint and positive-semidefinite operator.
		Under the conditions of Lemma \ref{lemma:cross_cov_functional}, $\mathcal{U}$ is a compact operator.
	\end{lemma}
	The proof of Lemma \ref{lemma:composite_cross_cov} is provided in Appendix \ref{section:proof:lemma:composite_cross_cov}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{hsingTheoreticalFoundationsFunctional2015}), Lemma \ref{lemma:composite_cross_cov} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\xi_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathbb{H}$ such that $\mathcal{U} \xi_{(u)} = \kappa_{(u)}  \xi_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following theorem presents population-level PLS and Tucker's Criterion for our scalar-on-hybrid regression model and ensures that line \ref{alg:line:pls_direction} of Algorithm \ref{alg:population_pls} is well-defined under mild conditions.
	\begin{theorem}[Tucker's criterion]\label{theorem:population_PLS} Under the conditions of Lemma \ref{lemma:cross_cov_functional}, the constrained maximum
		\begin{equation*} 
			\max \limits_{\substack{ \Vert \xi \Vert_\mathbb{H}=1}} \operatorname{Cov}^2 \left(\langle W , \, \xi \rangle_\mathbb{H}, Y \right)
		\end{equation*} 
		is attained by the eigenfunction associated with the largest eigenvalue of the operator $\mathcal{U}$.
	\end{theorem}
	The proof of Theorem \ref{theorem:population_PLS} is provided in Appendix \ref{section:proof:theorem:population_PLS}.

	Finally, the following theorem states that the fitted values from hybrid PLS converge to those of ordinary linear regression in the mean-squared sense. This shows that hybrid PLS, as a dimension-reduction technique, can effectively capture the predictive power of a full linear model when a sufficient number of components is used.
	\begin{theorem}[$L^2$ Convergence of Hybrid PLS at Population Level]\label{thm:hybrid_pls_convergence}
		Let $Y_{\mathrm{PLS}, L} = \sum_{l=1}^L \nu^{[l]} \rho^{[l]}$ be the Hybrid PLS fitted value with $L$ components. Then, the Hybrid PLS fitted value converges to $Y$ in the mean-squared sense:
		\begin{equation*}
			\lim_{L \to \infty} \mathbb{E}\left[ \| Y_{\mathrm{PLS},L } - Y  \|_2^2 \right] = 0
		\end{equation*}
	\end{theorem}
	The proof of Theorem \ref{thm:hybrid_pls_convergence} is provided in Appendix \ref{section:proof:thm:hybrid_pls_convergence}.

	\subsection{Geometric properties}\label{section:sub:geom}
	A fundamental property of partial least squares,
	as seem in Definition \ref{def:population_pls} and Proposition \ref{prop:residualization_equiv_eigen},
	is that between iterations, its derived directions are orthonormal and PLS scores are orthogonal. Our regularized estimates preserve this property, with respect to a modified inner product that incorporates the roughness penalty, defines as follows:
	\begin{definition}[Roughness-sensitive inner product]\label{def:hybrid_inner_product_roughness}
		Given two hybrid predictors $W_1 = (X_{11}, \ldots, X_{1K}, \mathbf{Z}_1)$ and $W_2 = (X_{21}, \ldots, X_{2K}, \mathbf{Z}_2)$, both elements of $\mathbb{H}$ as defined in Definition \ref{def:hybrid_predictor}, and a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, the roughness-sensitive inner product between $W_1$ and $W_2$ is defined as:
		\begin{equation}		\label{eq: hybrid inner product_roughness}
			\langle W_1, W_2\rangle_{\mathbb{H}, \Lambda}
			:=
			\sum \limits_{k=1}^K \int_0^1 X_{1k}(t) X_{2k}(t) \, dt
			+
			\sum \limits_{k=1}^K \lambda_k \int_0^1 X^{\prime \prime}_{1k}(t) X^{\prime \prime}_{2k}(t) \, dt
			+
			\mathbf{Z}_1^\top \mathbf{Z}_2.
		\end{equation}
	\end{definition}
	Based on this inner product, the following proposition states that the PLS component directions estimated from Proposition  \ref{proposition:eigen_regul} are orthonormal.
	\begin{proposition}[Orthonormality of estimated PLS component directions]\label{proposition: modified orthnormality of PLS components}
		The PLS component directions $
		\widehat{\xi}^{[1]}, \widehat{\xi}^{[2]}, \ldots, \widehat{\xi}^{[L]}
		$, estimated via Proposition \ref{proposition:eigen_regul} with a roughness penalty matrix $\Lambda = \operatorname{blkdiag}(\lambda_1 I_M, \ldots, \lambda_K I_M, 0_{p \times p})$, are mutually orthonormal with respect to the inner product $\langle \cdot, \cdot \rangle_{\mathbb{H}, \Lambda}$. That is,
		\begin{equation*}
			\langle \widehat{\xi}^{[l_1]}, \widehat{\xi}^{[l_2]} \rangle_{\mathbb{H}, \Lambda}
			= \mathbbm{1}(l_1 = l_2), \quad l_1, l_2 = 1, \ldots, L.
		\end{equation*}
	\end{proposition}
	The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.

@@

		Recall the residualization definitions (for fixed \(l\ge 2\)):
		\[
		W^{[l]} \;=\; W - \sum_{j=1}^{\,l-1} \rho^{[j]}\,\delta^{[j]},
		\qquad
		Y^{[l]} \;=\; Y - \sum_{k=1}^{\,l-1} \nu^{[k]}\,\rho^{[k]},
		\]
		where
		\[
		\rho^{[j]}=\langle W^{[j]},\xi^{[j]}\rangle,\quad
		\delta^{[j]}=\frac{\mathbb{E}[\rho^{[j]} W^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]},
		\nu^{[j]}=\frac{\mathbb{E}[\rho^{[j]} Y^{[j]}]}{\mathbb{E}[(\rho^{[j]})^2]}.
		\]
		Since \(W,Y\) are centered, 
		so are $W^{l}, Y^{l}$.
		Thus covariances are expectations of products.
		Fix any \(w\in\mathbb{H}\).  Using linearity,
			\operatorname{Cov}\!\big(\langle W^{[l]},w\rangle,\;Y^{[l]}\big)
			&= \mathbb{E}\Big[\big(\langle W,w\rangle - \sum_{j=1}^{l-1} \rho^{[j]}\langle\delta^{[j]},w\rangle\big)
			\big(Y - \sum_{k=1}^{l-1} \nu^{[k]}\rho^{[k]}\big)\Big] \\
			\\&= \mathbb{E}[\langle W,w\rangle Y] 
			- \sum_{k=1}^{l-1} \nu^{[k]}\,\mathbb{E}[\langle W,w\rangle \rho^{[k]}]
			- \underbrace{
				\sum_{j=1}^{l-1} \langle\delta^{[j]},w\rangle\,\mathbb{E}[\rho^{[j]} Y]}_{:=S_1} \\
			&\qquad
			\underbrace{
